The Name of the Title Is Hope

### 2024-04-24 paper/paper.tex
text added

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Abstract goes here
\end{abstract}

@@

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), Sigma protocols remain a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems, 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZKSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in Helios, Belenois, and SwissPost voting systems. 
  However, the existing implementations of sigma protocol are not formally verified and 
  therefore offer no security guarantees. \textbf{Double check this and its purpose: Moreover, 
  the same code is written twice, once for the front-end and once for the back-end}.
  In this paper, we present a formal verification of sigma protocol in the Coq proof assistant. 
  We prove that our formalisation is (special) sound, complete, and (honest verifier) 
  zero-knowledge. Moreover, 
  we compile our Coq formalisation to WebAssembly code and Rust code, and 
  thereby solve the problem of writing the same code twice, once for the 
  front-end and once for the back-end. We demonstrate the applicability of our
  formalisation by encoding the cryptographic protocols implemented in 
  Helios voting systems. Our long terms goal is to provide a verified
  cryptographic library that can be readily used in 
  privacy-preserving voting systems.

\end{abstract}

@@

\section{Introduction}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), sigma protocol remains a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocols are used in Helios, Belenois, and SwissPost voting 
systems (\textbf{Look for more examples}). 
Moreover, recently ZKP community started a movement to standardise
the Sigma protocols.

One of the main reasons for the popularity of sigma protocols in 
privacy-preserving voting systems is their simplicity and well-understood
security.

Sigma protocols are a special case of
zero-knowledge proofs where the verifier is assumed to be honest. Sigma protocols
allow a prover to convince a verifier that they possess some knowledge without
revealing anything else about the knowledge itself. Sigma protocols are used in

\textbf{Introduce here that sigma protocols are efficient and simple and all 
other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
they possess some knowledge without revealing anything else about the knowledge itself.  
More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Okamoto protocol in the privacy-preserving voting systems, 
at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
Web Assembly and Rust.
